\bf On semidefinite-representable sets over valuation fields

### 2025-01-21 article/paper_padic_spec.tex
commit by Simone
footnote on rem 3.3

@@

\tableofcontents

@@

In this section we show that the image of a polyhedron by a linear mappingA is a polyhedron. 
We first prove the result in the cases of authomorphisms of $\OK^n$ and diagonal endomorphisms of $K^n$.
Then we use these particular cases to prove the result for projections of the form $(x_1,\dots,x_n) \mapsto (x_1,\dots, x_{n-1})$
and finally for the general case.

\begin{remark}
 First, let $f : K^n \to K^m$ be a linear map and $\PP \subset K^n$ be a polyhedron defined by 
$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, m_i(x)=0, \textrm{ for } i \in I, j \in J \right\rbrace$ 
for some finite sets $I \subset \N$ and $J \subset \mathbb{N}$ and $m_j, l_i \in K[x]_1$, for $i \in I$  and $j \in J$.
Then  $\PP = \PP_i \cap \PP_e$ where $\PP_i := \{x \in K^n : \val(l_i(x)) \ge 0, i = 1,\dots,d\}$
and $\PP_e := \{x \in K^n : m_j(x) = 0, j = 1,\dots,e\}$.

Thus, we have  $f(\PP) = f(\PP_i) \cap f(\PP_e)$.
However, $\PP_e$ is either empty or an affine subspace of $K^n$ and therefore 
$f(\PP_e)$ is either empty or an affine subspace of $K^m$, so it is a polyhedron.
Hence, as the class of polyhedron is closed under intersection to prove that
$f(\PP)$ is a polyhedron it is sufficient to prove that $f(\PP_i)$ is one.
\end{remark}

>>>>

\usepackage{geometry}
\geometry{
 a4paper,
 %total={170mm,257mm},
 left=35mm,
 top=40mm,
 bottom=20mm
}

@@

%\tableofcontents

@@

In this section we show that the image of a polyhedron by a linear mapping is a polyhedron. 
We first prove the result in the cases of authomorphisms of $\OK^n$ and diagonal endomorphisms of $K^n$.
Then we use these particular cases to prove the result for projections of the form
$(x_1,\dots,x_n) \mapsto (x_1,\dots, x_{n-1})$ and finally for the general case.

\begin{remark}
  First, let $f : K^n \to K^m$ be a linear map and let $\PP \subset K^n$ be a polyhedron defined by 
$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, m_i(x)=0, \textrm{ for } i \in I, j \in J \right\rbrace$ 
  for some finite sets $I \subset \N$ and $J \subset \mathbb{N}$ and $m_j, l_i \in K[x]_1$, for $i \in I$  and
  $j \in J$.
Then  $\PP = \PP_i \cap \PP_e$ where $\PP_i := \{x \in K^n : \val(l_i(x)) \ge 0, i = 1,\dots,d\}$
and $\PP_e := \{x \in K^n : m_j(x) = 0, j = 1,\dots,e\}$.

Thus, we have\footnote{\simone{attention, ça est vrai si $f$ est injective, en général on a seulement
$\subset$}}  $f(\PP) = f(\PP_i) \cap f(\PP_e)$.
However, $\PP_e$ is either empty or an affine subspace of $K^n$ and therefore 
$f(\PP_e)$ is either empty or an affine subspace of $K^m$, so it is a polyhedron.
Hence, as the class of polyhedron is closed under intersection to prove that
$f(\PP)$ is a polyhedron it is sufficient to prove that $f(\PP_i)$ is one.
\end{remark}
